{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2017-10-09 sftrends_manu.Rnw
prddat fig is good now

<<prddat, fig.cap = 'Model predictions.', fig.height = 8, fig.width = 8>>=
library(tidyverse)
library(grid)
source('R/funcs.R')

data(mods)

toplo <- mods %>% 
  mutate(
    anns = map(data, annual_agg)
  ) %>% 
  select(-data, -flovar) %>% 
  unnest %>% 
  group_by(resvar) %>% 
  nest %>% 
  mutate(
    plts = map(data, function(x){

      p <- ggplot(x, aes(x = date, y = bt_fits, group = Site_Code, colour = Site_Code)) +
        geom_point(alpha = 0.7) + 
        geom_line(aes(y = bt_norm)) +
        facet_wrap(~ Location, ncol = 1, scales = 'free_y') + 
        theme_minimal() + 
        theme(
          legend.position = 'none', 
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(), 
          panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
          strip.text.x = element_text(size = 10)
          )

@@

pleg <- ggplot(toplo$data[[1]], aes(x = date, y = bt_fits, group = Site_Code, colour = Site_Code)) +
  geom_point(alpha = 0.7) + 
  geom_line(aes(y = bt_norm)) +
  theme_minimal() + 
  guides(colour = guide_legend(ncol = 2))
pleg <- g_legend(pleg)

@@

# (2, 3), (3, 3)
pA <- ggplot_gtable(ggplot_build(toplo$plts[[1]]))
pB<- ggplot_gtable(ggplot_build(toplo$plts[[2]]))
pC <- ggplot_gtable(ggplot_build(toplo$plts[[3]]))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[c(2:3)], pC$widths[c(2:3)])
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(
  arrangeGrob(
    arrangeGrob(pA, left = textGrob(ylab1, rot = 90)),
    arrangeGrob(pC, left = textGrob(ylab3, rot = 90)), 
    ncol = 1
  ), 
  arrangeGrob(
    arrangeGrob(pB, left = textGrob(ylab2, rot = 90)), 
    pleg, ncol = 1
  ), 
  ncol = 2
  )

@@

# (2, 3), (3, 3)
pE <- ggplot_gtable <- (ggplot_build(p5))
pH   <- ggplot_gtable(ggplot_build(p8))
maxWidth = unit.pmax(pE$widths[2:3], pH$widths[c(2:3)])
pE$widths[2:3] <- maxWidth
pH$widths[2:3] <- maxWidth

>>>>

<<prddat, fig.cap = 'Model predictions for ten stations grouped by nitrogen analyte and geographic location in the Delta region (locations in \\cref{fig:delt_map}).  Results are annually-averaged for each water year from October to September.  Points are model predictions and lines are flow-normalized predictions.', fig.height = 8, fig.width = 8>>=
data(mods)
data(delt_dat)

cols <-  brewer.pal(9, 'Blues')[c(4:9)] %>% 
  colorRampPalette(.)

stat_meta <- delt_dat %>% 
  dplyr::select(Site_Code, Location) %>% 
  unique %>% 
  mutate(
    Location = factor(Location, 
           levels = c('Delta', 'Middle', 'Suisun'), 
           labels = c('Peripheral', 'Interior', 'Suisun')
    )
  ) %>% 
  arrange(Location, Site_Code) %>% 
  mutate(
    colv = c(cols(4), cols(3), cols(3)), 
    pts = c(1:10), 
    shps = c(c(16, 17, 18, 15), c(16:18), c(16:18))
  )

toplo <- mods %>% 
  mutate(
    anns = map(data, annual_agg), 
    Location = factor(Location, 
                      levels = c('Delta', 'Middle', 'Suisun'), 
                      labels = c('Peripheral', 'Interior', 'Suisun')
                      )
  ) %>% 
  left_join(stat_meta, by = c('Site_Code', 'Location')) %>% 
  select(-data, -flovar) %>% 
  unnest %>% 
  group_by(resvar) %>% 
  nest %>% 
  mutate(
    plts = map(data, function(x){

      p <- ggplot(x, aes(x = date, y = bt_fits, group = Site_Code)) +
        geom_point(alpha = 0.9, col = x$colv, pch = x$shps) + 
        geom_line(aes(y = bt_norm), col = x$colv) +
        facet_wrap(~ Location, ncol = 1, scales = 'free_y') + 
        theme_minimal() + 
        theme(
          legend.position = 'none', 
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(), 
          panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
          strip.text.x = element_text(size = 10)
          )

@@

peri <- stat_meta %>% 
  filter(Location == 'Peripheral')
inte <- stat_meta %>% 
  filter(Location == 'Interior') 
suis <- stat_meta %>% 
  filter(Location == 'Suisun')

perileg <- ggplot(peri, aes(x = pts, y = pts, colour = Site_Code, shape = Site_Code)) +
  geom_point() +
  geom_line() +
  theme_minimal() + 
  scale_colour_manual(values = peri$colv, name = 'Peripheral') +
  scale_shape_manual(values = peri$shps, name = 'Peripheral') +
  theme(legend.position = 'top')
perileg <- g_legend(perileg)

inteleg <- ggplot(inte, aes(x = pts, y = pts, colour = Site_Code, shape = Site_Code)) +
  geom_point() +
  geom_line() +
  theme_minimal() + 
  scale_colour_manual(values = inte$colv, name = 'Interior') +
  scale_shape_manual(values = inte$shps, name = 'Interior') +
  theme(legend.position = 'top')
inteleg <- g_legend(inteleg)

suisleg <- ggplot(suis, aes(x = pts, y = pts, colour = Site_Code, shape = Site_Code)) +
  geom_point() +
  geom_line() +
  theme_minimal() + 
  scale_colour_manual(values = suis$colv, name = 'Suisun') +
  scale_shape_manual(values = suis$shps, name = 'Suisun') +
  theme(legend.position = 'top')
suisleg <- g_legend(suisleg)

@@

pA <- ggplot_gtable(ggplot_build(toplo$plts[[1]]))
pB<- ggplot_gtable(ggplot_build(toplo$plts[[2]]))
pC <- ggplot_gtable(ggplot_build(toplo$plts[[3]]))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[c(2:3)], pC$widths[c(2:3)])
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(
  arrangeGrob(
    arrangeGrob(pA, left = textGrob(ylab1, rot = 90)),
    arrangeGrob(pC, left = textGrob(ylab3, rot = 90)), 
    ncol = 1
  ), 
  arrangeGrob(
    arrangeGrob(pB, left = textGrob(ylab2, rot = 90)), 
    arrangeGrob(perileg, inteleg, suisleg, ncol = 1, top = textGrob('\nStations'))
  ), 
  ncol = 2
  )

@@

# (2, 3), (3, 3)
pE <- ggplot_gtable(ggplot_build(p5))
pH   <- ggplot_gtable(ggplot_build(p8))
maxWidth = unit.pmax(pE$widths[2:3], pH$widths[c(2:3)])
pE$widths[2:3] <- maxWidth
pH$widths[2:3] <- maxWidth

### 2017-10-09 sftrends_manu.tex
a pointless figure
prddat fig is good now

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
  \\\\{\textit {\normalsize Current address: Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\ Version Date:   Tue Oct 3 12:05:52 2017 -0700
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption[Model predictions]{Model predictions.}\label{fig:prddat}
\end{figure}

@@

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gList(structure(list(data = list(structure(list(colour = c("{}\#66C2A5"{}, : only 'grobs' allowed in "{}gList"{}}}\end{kframe}

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
  \\\\{\textit {\normalsize Current address: Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\ Version Date:   Fri Oct 6 15:33:58 2017 -0700
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption{Model predictions for ten stations grouped by nitrogen analyte and geographic location in the Delta region (locations in \cref{fig:delt_map}).  Results are annually-averaged for each water year from October to September.  Points are model predictions and lines are flow-normalized predictions.}\label{fig:prddat}
\end{figure}

@@

{\centering \includegraphics[width=0.9\textwidth]{figs/clmchl-1}

\caption{Trends in clam abundance and \ac{chla} concentration from 1976 to 2013 at station D7 in Suisun Bay.  Invasion by \textit{Potamocorbula amurensis} clams in the late 1980s and reduction of \textit{Corbicula fluminea} was shown by changes in clam density (a, annual means), with biomass linked to salinity (b).  A decrease in \ac{chla} concentration was also observed by changes in annual (c) and seasonal trends (f) based on \ac{wrtds} results.  Reductions in \ac{chla} concentration were coincident with an increase in SiO$_2$ and \ac{din} concentrations (d, e), with the greatest increases in August (g, h). A significant ($p < 0.001$) relationship between clam biomass and \ac{chla} concentration is shown in subfigure (i).  Flow relationships with \ac{chla} concentration shown by \ac{wrtds} have also changed over time (j, observations from June).}\label{fig:clmchl}
\end{figure}
